Forecasting biodiversity in breeding birds using best practices

### 2017-12-09 manuscript/draft.Rmd
explain future predictions

**Future environmental projections.** We made long term forecasts from 2014-2050
using the CMIP5 multi-model ensemble dataset as the source for climate
variables [@brekke2013]. Precipitation and temperature from 37 downscaled model
runs [@brekke2013, see Table S1] using the RCP6.0 scenario were averaged
together to create a single ensemble used to calculate the bioclimatic variables
for North America. For NDVI we used the per-site average values from 2000-2013
as a simple forecast. For observer effects (see below) each site was set to have
zero observer bias.

>>>>

**Future environmental projections.** In addition to the analyses presented
here, we have also generated and archived long term forecasts from 2014-2050.
This will allow future researchers to assess the performance of our six models
on longer time horizons as more years of BBS data become available.
Precipitation and temperature were forecast using the CMIP5 multi-model ensemble
dataset [@brekke2013]. 37 downscaled model runs [@brekke2013, see Table S1]
using the RCP6.0 scenario were averaged together to create a single ensemble
used to calculate the bioclimatic variables for North America. For NDVI, we used
the per-site average values from 2000-2013 as a simple forecast. For observer
effects (see below), each site was set to have zero observer bias. The
predictions have been archived at [@zenodoPredict].
